---
title: "Homework 5"
output: github_document
---

```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis", 
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in data

```{r}
homicide_df = 
  read.csv("./data/homicide-data.csv") %>% 
  janitor::clean_names()
```

This dataset is from the Washington Post, which mapped over 52,000 homicides and any resulting arrests within 50 of the largest cities in America. Key variables in this dataset include Report date; Victim name, age, and sex; City; State; Latitude and longitude; and the Disposition. There are `r nrow(homicide_df)` rows and `r ncol(homicide_df)` columns in this raw dataset. 

Add variables "city_state", "resolved", and summarize total homicides and total unresolved homicides within cities. 

```{r}
homicide_df =
  homicide_df %>% 
  unite("city_state", city:state, sep = "_", remove = TRUE) %>% 
  mutate(
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved")
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
#removing presumably data entry error for "Tulsa_AL"

aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarise(
    total_hom = n(),
    unsolved_hom = sum(resolved == "unsolved")
  )
```

For Baltimore_MD, estimate proportion of homicides that are unsolved. 

```{r}
balt_prop = 
  prop.test(
    aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(unsolved_hom), 
    aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(total_hom)) %>% 
  broom::tidy()

balt_prop %>% pull(estimate)
balt_prop %>% pull(conf.low) 
balt_prop %>% pull(conf.high)
```

Run prop.test for each city, extract the proportion and CIs for each:

```{r}
results_df = 
  aggregate_df %>%
  mutate(
    prop_tests = map2(.x = unsolved_hom, .y = total_hom, ~prop.test(x = .x, n = .y)), 
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)

results_df
```

Create plot for estimates and CIs:

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

Create dataframe for the provided longitudinal study data with data from all participants across the 20 csv files. 

```{r}
path_df = 
  tibble(
    path = list.files("ls_data")
  ) %>% 
  mutate(path = str_c("ls_data/", path),
         data = map(path, read_csv)
         ) %>% 
  unnest(data)
```

Tidy the dataframe:

```{r}
l_study_df = 
  path_df %>% 
  rename(file_name = path) %>% 
  mutate(
    #creating subject IDs
    subject_id = file_name,
    subject_id = str_remove(subject_id, "ls_data/"),
    subject_id = str_remove(subject_id, ".csv"),
    subject_id = str_replace(subject_id, "con", "c"),
    subject_id = str_replace(subject_id, "exp", "e"),
    #creating study arm variable
    study_arm = case_when(
      subject_id == c("c_01", "c_02", "c_03", "c_04", "c_05", 
                    "c_06", "c_07", "c_08", "c_09", "c_10") ~ "control",
      subject_id == c("e_01", "e_02", "e_03", "e_04", "e_05", 
                    "e_06", "e_07", "e_08", "e_09", "e_10") ~ "experimental")
  ) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week_number",
    names_prefix = "week_",
    values_to = "observed_values"
  ) %>% 
  select(subject_id, study_arm, week_number, observed_values, file_name)
```

Make a spaghetti plot showing observations on each subject over time. 

```{r}
l_study_df %>% 
  ggplot(aes(x = week_number, y = observed_values, color = study_arm)) + 
  geom_point() +
  geom_path(aes(group = subject_id), alpha = 0.4) + 
  labs(title = "Observations for each study subject over time") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(vjust = 0.5, hjust = 1),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 9)
    )
```

Looking at this plot, we can see that between the control and experimental arms - subjects in the control arm appeared to have greater observed values compared to those in the experimental arm of the study. Relatively few subjects in the control arm appear to have negative observed values - while several subjects in the experimental arms have negative values recorded. 

## Problem 3

Generate 5000 datasets from normal distrib with n = 50, sigma = 5, and mu = 0. 

```{r}

```

For each dataset, save μ^ and the p-value arising from a test of H:μ=0 using α=0.05. 

Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of t.test.

Repeat the above for μ={1,2,3,4,5,6}, and complete the following:

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.

Make a plot showing the average estimate of μ^ on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ^ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ^ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?
