---
title: "Homework 5"
output: github_document
---

```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis", 
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in data

```{r}
homicide_df = 
  read.csv("./data/homicide-data.csv") %>% 
  janitor::clean_names()
```

This dataset is from the Washington Post, which mapped over 52,000 homicides and any resulting arrests within 50 of the largest cities in America. Key variables in this dataset include Report date; Victim name, age, and sex; City; State; Latitude and longitude; and the Disposition. There are `r nrow(homicide_df)` rows and `r ncol(homicide_df)` columns in this raw dataset. 

Add variables "city_state", "resolved", and summarize total homicides and total unresolved homicides within cities. 

```{r}
homicide_df =
  homicide_df %>% 
  unite("city_state", city:state, sep = "_", remove = TRUE) %>% 
  mutate(
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved")
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
#removing presumably data entry error for "Tulsa_AL"

aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarise(
    total_hom = n(),
    unsolved_hom = sum(resolved == "unsolved")
  )
```

For Baltimore_MD, estimate proportion of homicides that are unsolved. 

```{r}
balt_prop = 
  prop.test(
    aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(unsolved_hom), 
    aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(total_hom)) %>% 
  broom::tidy()

balt_prop %>% pull(estimate)
balt_prop %>% pull(conf.low) 
balt_prop %>% pull(conf.high)
```

Run prop.test for each city, extract the proportion and CIs for each:

```{r}
results_df = 
  aggregate_df %>%
  mutate(
    prop_tests = map2(.x = unsolved_hom, .y = total_hom, ~prop.test(x = .x, n = .y)), 
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)

results_df
```

Create plot for estimates and CIs:

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

Using longitudinal study data. Create a tidy dataframe with data from all participants (subject ID, arm, and observations over time).

```{r}
path_df = 
  tibble(
    path = list.files("ls_data")
  ) %>% 
  mutate(path = str_c("ls_data/", path)
         )

read_csv(path_df$path[[1]])
#How to do across all 20 paths, data = map(.......) in mutate function
```

Dataframe containing all file names

Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe. Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary. 

Pivot --- week (#) and then obs next to it!!

```{r}

```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups

## Problem 3

Generate 5000 datasets from normal distrib with n = 50, sigma = 5, and mu = 0. 

```{r}

```

For each dataset, save μ^ and the p-value arising from a test of H:μ=0 using α=0.05. 

Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of t.test.

Repeat the above for μ={1,2,3,4,5,6}, and complete the following:

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.

Make a plot showing the average estimate of μ^ on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ^ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ^ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?
